\documentclass{template}

\usepackage[left=0.3 in,top=0.3in,right=0.3 in,bottom=0.3in]{geometry}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{\href{https://linktr.ee/princesanjivy}{SANJIVY KUMARAVEL}}
\address{+91 9443376775 \\ sanjivy.android@gmail.com}

\begin{document}
\begin{rSection}{Education}
{\bf Bachelor of Technology (Hons) in Information Technology} \hfill {2018 - 2022}
\\ 
Pondicherry Engineering College, Puducherry \\
CGPA : 8.40/10

%{\textbf{CBSE, Class XII}} \hfill 2017 - 2018\\
%The Study, Puducherry \\
%CGPA : 8.20/10

\end{rSection}

\begin{rSection}{EXPERIENCE}
\textbf{Software Engineer at Striim, Chennai} \hfill July 2022 - Present \\
Striim is a distributed data integration and intelligence platform that also offers a cloud-based fully managed SaaS platform on all three CSPs (GCP, Azure, AWS). I work as part of Striim's SaaS team, in my role,

\begin{itemize}
    \item I contributed to a feature project that involved integrating Azure and AWS private link with the Striim SaaS platform with my teammates.

    \item I have individually contributed to multiple feature projects, including the recent project which is adding SCIM and SAML integration of Azure with our SaaS application.

    \item I enhanced our internal release deployment tool for onboarding Striim platform solutions to our SaaS application.

    \item I have established an automation pipeline setup for the QA team to easily run their testsuites on spinnaker within the same internal tool.

    \item I built an internal microservice around the Kubernetes API as a wrapper with custom parameters to address our internal use case.

    \item I have also worked on cleaning up unused resources by writing fault-tolerance workflows in Uber Cadence and deploying them across all CSPs, ultimately helping us reduce CSPs costs.

    \item Apart from feature projects, I have ad-hocly worked on enhancing existing APIs, refactoring code, delivering presentation demos on completed projects for other team members, and writing documentation.
\end{itemize}

\textbf{Software Engineer Intern at Striim, Chennai} \hfill January 2022 - July 2022 \\
I was a member of the SaaS team during my internship. Throughout this period, I familiarized myself with our internal microservice-based architecture developed in GoLang using Gin. Initially, I was assigned QA tasks, where I implemented automation for Cypress using JavaScript, I performed manual UI testing and developed a solution for uploading test results as reports to Jira's X-Ray using Python and Jira's REST APIs. After completing my internship, I transitioned to the SaaS development team from the QA team. 

\textbf{Python Instructor at Ocean Academy, Puducherry} \hfill October 2021 - May 2022 \\
As a Python Instructor, I taught students the fundamentals of Python programming language along with its web-framework Flask. Through my guidance, students gained a strong understanding of the language and were able to develop practical skills for real-world applications.

\textbf{MLOps Intern at Yuvabe, Puducherry} \hfill June 2021 - September 2021 \\
I helped the team in writing FastAPI wrappers for their existing ML model scripts and deployed them in Google Cloud Run, also made a front-end in ReactJs for displaying the inferences.

\textbf{Software Developer Intern at Ilahi Technologies, Puducherry} \hfill December 2020 - April 2021 \\
I was responsible for developing Android and web apps using Flutter for client projects. During my tenure, I worked on three Android apps and a web app for admin panel. Through my work, I gained valuable experience in app development and honed my skills in Flutter and Firebase. My contributions helped Ilahi Technologies to deliver high-quality solutions to their clients.

\end{rSection} 

\begin{rSection}{SKILLS}
\begin{itemize}
    \item \textbf{Python}, \textbf{Go}, Gin, FastAPI, Flutter, Flask, Websockets, Git/Github, REST API design, 

    \item \textbf{Firebase} (Firestore \& Functions), MySQL, MongoDB Atlas, \textbf{GCP} (GKE, Cloud Run), \textbf{Azure} (Entra ID, Functions), \textbf{AWS} (EKS, Lambda, PrivateLink), \LaTeX.
\end{itemize}

\end{rSection}

\begin{rSection}{PERSONAL PROJECTS}

\textbf{\href{https://github.com/princesanjivy/pycare-api}{PyCare API}} \\
I spearheaded the development of the \href{https://sites.google.com/view/dscpec/pudhuvai-care}{Pudhuvai Care} app and its corresponding REST API for the Puducherry Health Government. Leveraging Flutter for the app's user interface and Python's FastAPI framework for the backend, the deployed application on Heroku now offers an efficient solution for monitoring hospital details in Pondicherry. \\
\textbf{\textit{Technologies used}}: Flutter, Python (FastAPI), Heroku, Web Scraping Techniques

\textbf{Android Applications} \\
I have created several Android applications, some of which have garnered over 500+ downloads on the Google Play Store.

\begin{itemize}

\item \textbf{\href{https://github.com/princesanjivy/moviestylefonts}{Movie Style Fonts}} \\ 
This Android and web application enables users to generate movie poster font styles with their own text. \\
\textbf{\textit{Technologies used}}: Flutter, HTML, CSS, JavaScript (P5.js library)

\item \textbf{\href{https://play.google.com/store/apps/details?id=com.princeappstudio.ptu_cgpa_tracker}{PTU CGPA Tracker}} \\ 
The PTU CGPA Tracker app simplifies the calculation of CGPA for PTU students based on their semester results. With an intuitive design, students can enter their grades while the app handles the calculations using stored credit scores for each subject. This app, utilized by numerous students, has been designed to enhance user experience. \\
\textbf{\textit{Technologies used}}: Flutter, Firebase, Figma (UI/UX)

\item \textbf{Repostaffs} \\ 
Repostaffs is a mobile application designed to monitor the daily contributions of staff members in a specific hair salon. Developed as a freelance project for the Toni and Guy salon in Pondicherry, the application features two portals: one for staff members and another for admin. Staff members can update their consultation/work status, mark attendance via QR codes, while the admin can manage staff, generate reports, and oversee salon operations. \\
\textbf{\textit{Technologies used}}: Flutter, Firebase, Excel

\end{itemize}

\textbf{Driver Drowsiness Detection System} \\
For my final-year project, I contributed to the development of an Android application and curated datasets for the model. By extracting images from driver videos, we successfully constructed a robust system to detect driver drowsiness. Our implementation employed the Flutter framework for the application's user interface and utilized Python for the backend logic. Our project has successfully created a tool to help prevent accidents caused by driver fatigue. \\
\textbf{\textit{Technologies used}}: Python (FastAPI)

\textbf{Canteen Management System} \\
I developed a web-based administration application for Brewery company administrators and an Android app for canteen operations. Created as a freelance project for a government-assisted Brewery company in Lao, the Android app is utilized on POS machines for functions such as order placement, inventory management, revenue tracking, and employee/user management. The web admin application empowers administrators to oversee multiple canteens, manage user access, generate reports, and access revenue dashboards. This project, from architectural design to building the Firebase Firestore backend and deploying the application on Hostinger's VPC, was a complex real-time use case that spanned approximately 6 months. \\
\textbf{\textit{Technologies used}}: Flutter, Python (FastAPI), MySQL, Hostinger

\end{rSection}

\begin{rSection}{ACCOMPLISHMENTS}
\textbf{Website design} \\
Awarded 1st prize in online 24hrs web designing challenge conducted by Kalasalingam Academy of Research and Education.

\textbf{Android app development} \\
Awarded 3rd prize in National Level Android app development contest conducted by Saveetha Engineering College.

\textbf{Code-a-thon} \\
Awarded 2nd prize in Inter-college Technical Symposium conducted by department of CSE, Pondicherry Engineering College.

\textbf{Code-a-thon} \\
Awarded 3rd prize in Inter-college Technical Symposium conducted by department of CSE, Pondicherry Engineering College.

\end{rSection}

\begin{rSection}{LINKS}
\href{https://github.com/princesanjivy}{Github},
\href{https://princesanjivy-portfolio.web.app/}{Portofolio},
\href{https://play.google.com/store/apps/dev?id=6439925551269057866}{Play Store},
\href{https://www.hackerrank.com/profile/sanjivy_android}{Hackerrank},
\href{https://www.instagram.com/princesanjivy}{Instagram}.

\end{rSection}

\begin{rSection}{LANGUAGES}
Tamil, English.

\end{rSection}

\begin{rSection}{PERSONAL SKILLS}
Problem solver, Interactive person, Leader, Instructor, Team player, Creative thinker,  Self-motivated.

\end{rSection}



\end{document}
